---
title: Hello Python & R
author: Rey Ylagan
date: '2021-05-07'
slug: hello-world
categories:
  - R
  - Python
tags:
  - Reticulate
description: 'Learning how to incororate R and Python'
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE, eval = TRUE,fig.align="center",warning=FALSE,message=FALSE,fig.width=8, fig.height=5, linewidth=60)
options(tibble.width = 100,width = 100)

```


```{r}
library(reticulate)
```
Today we will be learning the reticulate packedge in R and how to use Python in the same R Markdown file! 

### Variable Assignment
```{r}
#This is a R Code Chunk
R_Var <- "Hello I was made in R"
```
Here is a variable assignment in R


```{python}
#This is a Python Code Chunk
Py_Var = "Heyo I was made in Python"
```
Here is variable assignment in Python


### Acessing Different Variables 
```{python}
#Python Code Chunk
print(r.R_Var)
print(Py_Var)
```
*We can acess both R and Python variables together the same code chunk! In a Python Code chunk, to access R variables a prefix of r. is needed: `r.<R-Variable-Name>`*

```{r}
#R code chunk
cat( R_Var )
cat( py$Py_Var )
```
*This can also be done in reverse! So if you want to access a Python variable in R, a prefix of py$ is needed: `py$<R-Variable>`*


### Example using Reticulate
For this example we will be getting data input from Python and send it to R for easy plotting using `ggplot2`

I will be using the titanic [dataset](https://github.com/pandas-dev/pandas/blob/master/doc/data/titanic.csv)
```{python}
#Python Code Chunk
import pandas as pd
titanic = pd.read_csv("titanic.csv")
titanic.head(8)
```
Here we imported the Pandas Module in Python to grab the titanic dataset and store it in a Python variable. 


```{R}
library(tidyverse)
ggplot(py$titanic, aes(x=Pclass,y=Fare)) +
  geom_bar(stat="identity", fun=mean)
```
Using the Reticulate package in R this Python variable is accessed with the `py$`.  It was then mapped into ggplot to make a quick and easy plot!








